Parallel algorithm for solving multicriterial optimization problems using elements of machine learning

### 2025-04-06 2025/RSCD_MCO/RSD-2025.tex
MCO 2025 Структура + таблицы

\section{Introduction}

@@

@@

@@

@@

@@

@@

>>>>

\section{Introduction}
\label{sec1}

@@

\section{Problem statement}
\label{sec2}

\section{Computational scheme of the developed algorithm}
\label{sec3}

@@

\subsection{Block of the global search algorithm}

\subsection{Block for accumulating and reusing the information about current state of the search}

\subsection{Block for building the Pareto set estimation}

@@

\subsection{Block of  building the machine learning for estimation of the Pareto set}

@@

\subsection{Block for the choice of trial points and implementation of computational experiments}

\section{Results of computational experiments}
\label{sec4}

@@

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[ht]
\centering
\caption{Average number of trials per process}
\label{tab:1}
\resizebox{0.8\textwidth}{!}{%
\begin{tabular}{ccccccc}
\hline
\textbf{Number of processes}            & \textbf{1}      & \textbf{2}      & \textbf{4}      & \textbf{8}      & \textbf{16}    & \textbf{20}    \\ \hline
MGSA                                    & 2269.82         & 1385.02         & 746.57          & 373.36          & 202            & 143.52         \\
\textbf{MGSA   Linear SVC,  a = 0.05}   & \textbf{686.13} & \textbf{408.79} & \textbf{213.6}  & \textbf{111.85} & \textbf{70.95} & \textbf{62.16} \\
MGSA   Poly SVC, a = 0.05               & 909.59          & 544.19          & 278.62          & 153.64          & 95.37          & 77.94          \\
MGSA   RBF SVC, a = 0.04                & 652.74          & 446.84          & 233.81          & 119.84          & 72.36          & 62.37          \\
\textbf{MGSA   Dist, a = 0.01}          & \textbf{659.98} & \textbf{402.9}  & \textbf{211.33} & \textbf{112.38} & \textbf{70.79} & \textbf{62.00} \\
MGSA   NN 1 layer, a = 0.05             & 795.16          & 446.25          & 232.08          & 117.16          & 75.19          & 62.70          \\
\textbf{MGSA   NN 2 layers, a =   0.03} & \textbf{682.12} & \textbf{401.74} & \textbf{219.62} & \textbf{113.32} & \textbf{73.51} & \textbf{61.32} \\ \hline
\end{tabular}%
}
\end{table}

\begin{table}[ht]
\centering
\caption{Average HW Index in dependence on number of processes}
\label{tab:2}
\resizebox{0.8\textwidth}{!}{%
\begin{tabular}{ccccccc}
\hline
Number of processes                   & \textbf{1}      & \textbf{2}      & \textbf{4}      & \textbf{8}      & \textbf{16}     & \textbf{20}     \\ \hline
\textbf{MGSA}                         & \textbf{114.91} & \textbf{114.79} & \textbf{114.84} & \textbf{114.90} & \textbf{115.00} & \textbf{114.96} \\
MGSA   Linear SVC, a = 0.05           & 114.44          & 114.65          & 114.72          & 114.74          & 114.91          & 114.96          \\
\textbf{MGSA   Poly SVC,    a = 0.05} & \textbf{114.61} & \textbf{114.64} & \textbf{114.71} & \textbf{114.8}  & \textbf{114.95} & \textbf{115.01} \\
MGSA   RBF SVC,    a = 0.04           & 114.54          & 114.54          & 114.73          & 114.89          & 114.92          & 114.96          \\
MGSA   Dist, a = 0.01                 & 114.66          & 114.55          & 114.69          & 114.73          & 114.92          & 114.93          \\
MGSA   NN 1 layer, a = 0.05           & 114.77          & 114.61          & 114.72          & 114.81          & 114.96          & 114.98          \\
\textbf{MGSA   NN 2 layers, a = 0.03} & \textbf{114.74} & \textbf{114.54} & \textbf{114.71} & \textbf{114.76} & \textbf{114.98} & \textbf{115.01} \\ \hline
\end{tabular}%
}
\end{table}

@@

\section{Conclusion}
\label{sec5}
The research presents a parallel modification of the global search algorithm for solving multicriterial optimization problems. One of the features of the algo-rithm is the combination of the classic global search algorithm with machine learning methods. The combination of algorithms shows high efficiency in both sequential and parallel modifications. As the direction of further research it is planned to organize a number of experiments to solve applied problems and compare search efficiency with a number of third-party frameworks.
